---
output:
  md_document:
    variant: gfm
html_preview: false
---

<!-- README.md is generated from README.Rmd. Please edit that file -->
<!-- First time: run usethis::use_readme_rmd() to create a pre-commit hook that 
prevents from committing if the README.Rmd has changed, but has not been 
re-knitted to generate an updated README.md -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```


```{r echo=FALSE, results="hide", message=FALSE}
require(badger)

# modified badger function to all the Travis pipeline to run on other branches than the master
#
my_currentGitHubRef <- function(ref) {
	if (!is.null(ref)) {return(ref)}

	url <- desc::desc_get_field("URL")
	if (!grepl("gitHub", url, ignore.case = TRUE)) {
		stop("reference could not be determined by the DESCRIPTION' url")
	}

	url <- unlist(strsplit(url, ",\\s*"))
	url <- url[grepl("github", url, ignore.case = TRUE)][[1]]

	ref <- gsub("https://github.com/", "", url)
	ref
}

my_badge_travis <- function(ref = NULL, is_commercial = FALSE, branch = "master") 
{
    ref <- my_currentGitHubRef(ref)
    ext <- ifelse(is_commercial, "com/", "org/")
    svg <- paste0("https://travis-ci.", ext, ref, ".svg?branch=", branch)
    url <- paste0("https://travis-ci.", ext, ref)
    paste0("[![](", svg, ")](", url, ")")
}
```

## echoseq: Faithful replication and simulation of molecular and clinical data

<!-- Run for the R CMD checks, run usethis::use_github_actions() to set up the pipeline, possibly modify the .yaml file and then: -->
`r my_badge_travis("hruffieux/echoseq", branch = "devel")`
`r badge_github_actions("hruffieux/echoseq")` 
`r badge_license("GPL v3", url = "https://www.gnu.org/licenses/gpl-3.0")`
`r badge_devel("hruffieux/echoseq", "blue")`
`r badge_code_size("hruffieux/echoseq")`


## Overview

**echoseq** is an R package providing functions to emulate molecular quantitative
trait locus data, and clinical data associated with genetic variants under
user-specified association patterns. The data can be obtained by pure simulation 
or can replicate real datasets supplied by the user. Datasets simulated using 
**echoseq** may replace real datasets when these cannot be shared for diverse 
privacy reasons. The data generation schemes are based on generally accepted 
principles of population genetics (Hardy–Weinberg equilibrium, 
linkage-disequilibrium, natural selection, pleiotropic control, sparsity 
assumptions, epigenetic control, etc).


## Warning

**This is a development branch**, it is not guaranteed to be stable at any given
time and features are subject to change. Please use the [stable version](https://github.com/hruffieux/echoseq), unless you want to test and
report issues.

## Installation

To install, run the following commands in R:

``` r
if(!require(remotes)) install.packages("remotes")
remotes::install_github("hruffieux/echoseq", ref = "devel")
```

## License and authors

This software uses the GPL v3 license, see [LICENSE](LICENSE).
Authors and copyright are provided in [DESCRIPTION](DESCRIPTION).

## Issues

To report an issue, please use the [echoseq issue tracker](https://github.com/hruffieux/echoseq/issues) at github.com.
